How to compute the fusion product of MV cycles in type A

### 2021-05-16 draft.tex
qfj re semiinfty fusion as attr of single con com

    The \textbf{fusion of two spherical Schubert varieties} 
        \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA \,.

@@

By a theorem of Zhu 
\cite[Proposition 3.1.14]{zhu2016introduction}, $ \overline{\Gr}^{\lambda'} \ast_0 \overline{\Gr}^{\lambda''} $ is reduced and equal to  $ \overline{\Gr}^{\lambda' + \lambda''}$.

% Suppose that $ s \ne 0$.  
Moreover, if $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''}$ coming from transporting $ \Gr^{\lambda'} \times \Gr^{\lambda''} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $. 
% \acom{reference \cref{it:grs-gr}?} 
This open locus is a $ G(\CC[t])$-orbit
% .  The lattice description of $ \Gr_{0,s}^{\lambda', \lambda''}$ 
whose lattice description is given in \Cref{le:Grl1l2} below.
% \acom{Why $G(\CC[t])$. Because we are on the left side!}

@@

    For the $ s = 0$ fibre, a similar reasoning applies (or we can simply conclude by taking closure).
\end{proof}
    % \acom{why ``and so''? bc orbits are connected?}
    % \jcom{I turned this into a Lemma.}

@@

\begin{definition}
\label{def:klslice}
    The \textbf{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
\end{definition}
% 
\acom{we haven't defined $G_1$}

In modular terms, $\cW_\mu$ corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}. The lattice description of $ \cW_\mu \cap \Grth$ is given in Lemma \ref{le:Wmu} below. 
\acom{First lattice description that doesn't come for free?}
% 
% \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
% A: Ok thanks!
% 
\begin{definition} 
\label{def:inftyorbits}
    The \textbf{semi-infinite orbit} 
$$ S^\mu = N_-(\cK)t^\mu \subset \Gr $$ 
and the \textbf{fusion of  semi-infinite orbits} 
$$ 
    S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''} \to \AA \,.
$$  
\end{definition}
If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
$$
% S^{\mu', \mu''}_{0,s} = 
    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
$$
% TODO: resolve
% \jcom{Maybe we should introduce the $ L_{\mu', \mu''} $ notation, but I'm not sure it is necessary.}
On the other hand, if $ s = 0$, then the fibre $S^{\mu', \mu''}_{0,0} $ equals $ S^{\mu' + \mu''}$. 
% TODO: resolve
% \acom{changed $\mu$ to $\mu' + \mu''$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda', \lambda''} $}
% 
\jcom{I realized that this is not correct.  We can't just take the fusion here since we don't want to get the closure of these guys.  I will think about this further.}
\acom{Two definitions in one. Unlike for spherical schubs}

>>>>

    The \textbf{fusion of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} $.
    % $$ 
    %     \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA \,.
    % $$

@@

By \cite[Proposition 3.1.14]{zhu2016introduction}, $ \overline{\Gr}^{\lambda'} \ast_0 \overline{\Gr}^{\lambda''} $ is reduced and equal to  $ \overline{\Gr}^{\lambda' + \lambda''}$.
% Suppose that $ s \ne 0$.  
Moreover, if $s\ne0$, then in the fibre $\overline{\Gr}_{0,s}^{\lambda', \lambda''}$ we have the open locus $ \Gr_{0,s}^{\lambda', \lambda''}$ coming from transporting $ \Gr^{\lambda'} \times \Gr^{\lambda''} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $. 
% \acom{reference \cref{it:grs-gr}?} 
This open locus is a $ G(\CC[t])$-orbit
% .  The lattice description of $ \Gr_{0,s}^{\lambda', \lambda''}$ 
whose lattice description is given in \Cref{le:Grl1l2} below.
% \acom{Why $G(\CC[t])$. Because we are on the left side!}

\acom{Sorry I keep changing (abbreviating) ``By a theorem of Zhu'', but is the citation not sufficient?}

@@

    For the $ s = 0$ fibre, a similar reasoning applies (or we can simply conclude by taking closure).
\end{proof}

\acom{Does $M_m(\CC[t])\cap G\xT[t^{-1}] = \{g\in M(\CC[t]):\det g\in\CC[t]\setminus0\}$?}
    % \acom{why ``and so''? bc orbits are connected?}
    % \jcom{I turned this into a Lemma.}

@@

\begin{definition}
\label{def:klslice}
    The \textbf{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
\end{definition}
%

In modular terms, $\cW_\mu$ corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}. The lattice description of $ \cW_\mu \cap \Grth$ is given in Lemma \ref{le:Wmu} below. 
%

% \acom{First lattice description that doesn't come for free?}
% 
% \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
% A: Ok thanks!
% 
\begin{definition} 
\label{def:inftyorbits}
    The \textbf{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $. 
% and the \textbf{fusion of  semi-infinite orbits} 
% $$ 
% S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''} \to \AA \,.
% $$  
\end{definition}
\acom{Commented out fusion part for now. Unsure about defining it as the family whose 0 fibre is $S^{\mu' + \mu''}$ and whose generic fibre is $S^{\mu'}\times S^{\mu''}$ up to $\tau$. Baumann--Riche consider the attracting set of $C_\mu = \sqcup_{\mu' + \mu'' = \mu } m(\tilde C_{\mu',\mu''})$ where $\tilde C_{\mu',\mu''}$ is a connected component of fixed points in $\Grbd\tilde\times\Grbd$. Maybe we can consider the attracting set of just one of these?}

If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
$$
% S^{\mu', \mu''}_{0,s} = 
    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
$$
% TODO: resolve
% \jcom{Maybe we should introduce the $ L_{\mu', \mu''} $ notation, but I'm not sure it is necessary.}
On the other hand, if $ s = 0$, then the fibre $S^{\mu', \mu''}_{0,0} $ equals $ S^{\mu' + \mu''}$. 
% TODO: resolve
% \acom{changed $\mu$ to $\mu' + \mu''$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda', \lambda''} $}
%

\jcom{I realized that this is not correct.  We can't just take the fusion here since we don't want to get the closure of these guys.  I will think about this further.}
% \acom{Two definitions in one. Unlike for spherical schubs}
